Building socket-aware BPF programs

### 2018-10-31 paper/paper.tex
paper: Improve verifier intro

The BPF verifier must ensure that all BPF programs that are loaded into the
kernel are safe to execute. For accessing socket pointers, this requires
validation that memory accesses are within the bounds of the memory allocated
for the structure, and will not make any modifications to the socket fields
that would be incompatible with the core socket handling logic. This is
provided through extension of existing functionality which performs bounds
verification and offset conversion for programs operating on CGroups hooks.
Additionally, the underlying memory must remain associated with the socket for
the duration of accesses from the BPF program, which may be guaranteed by
taking a reference on sockets for the duration of their use. The following
sections explain how this is implemented through the introduction of a new
pointer type in the verifier, and through the extension of the verifier to
recognise assembly instructions that represent reference acquisition and
release.

>>>>

The BPF verifier must ensure that all BPF programs that are loaded into the
kernel are safe to execute. This necessitates verification of every path
through the program to ensure constraint such as that the program will halt,
and that any dereferencing of pointers is done in a safe and controlled manner.
For accessing socket pointers, this requires validation that memory accesses
are within the bounds of the memory allocated for the structure, and that no
modifications are made to the socket fields that would be cause the core socket
handling logic to get into a bad state. This is provided through extension of
existing functionality which performs bounds verification and offset conversion
for programs operating on CGroups hooks. Additionally, the underlying memory
must remain associated with the socket for the duration of accesses from the
BPF program, which may be guaranteed by taking a reference on sockets for the
duration of their use. The following sections explain how this is implemented
through the introduction of a new pointer type in the verifier, and through the
extension of the verifier to recognise assembly instructions that represent
reference acquisition and release.
